Towards open collaboration in biomedical and health research: A protocol for a scoping review of open collaboration

### 2025-03-18 doc/paper.qmd
chore: :wrench: add ORCID and affiliation URLs (#114)
Closes #109, closes #110

---
title: "Towards open collaboration in biomedical and health research: An open collaborative scoping review"
date: last-modified
author:
  - name: Mario Garcia
    affiliations:
      - ref: ku
  - name: Daniel B. Ibsen
    affiliations:
      - ref: sdca
      - ref: au
  - name: Luke W. Johnston
    affiliations:
      - ref: sdca
      - ref: au
affiliations:
  - id: sdca
    name: Steno Diabetes Center Aarhus
    country: Denmark
  - id: au
    name: Aarhus University
    country: Denmark
  - id: ku
    name: Copenhagen University
    country: Denmark
format:
  html: default
  academic-typst:
    section-numbering: "1.1.1"
    columns: 2
    papersize: a4
    margin:
      x: 2cm
      y: 2cm
format-links:
  - html
  - format: academic-typst
    text: PDF
    icon: file-pdf
abstract: |
  **Background**: Greater, more extensive collaboration is increasingly needed
  in the modern research environment, often to the level of team-based science.
  Combined with this need is the emphasize on doing more open science. However,
  there seems to be less attention on the overlap between open science and
  collaboration.

>>>>

---
title: "Towards open collaboration in biomedical and health research: An open collaborative scoping review"
date: last-modified
author:
  - name: Mario Garcia
    orcid: "0000-0002-3376-9460"
    affiliations:
      - ref: ku
  - name: Daniel B. Ibsen
    orcid: "0000-0002-7038-4770"
    affiliations:
      - ref: sdca
      - ref: au
  - name: Luke W. Johnston
    orcid: "0000-0003-4169-2616"
    affiliations:
      - ref: sdca
      - ref: au
affiliations:
  - id: sdca
    name: Steno Diabetes Center Aarhus
    country: Denmark
    url: "https://www.stenoaarhus.dk/"
  - id: au
    name: Aarhus University
    country: Denmark
    url: "https://www.au.dk/"
  - id: ku
    name: Copenhagen University
    country: Denmark
    url: "https://www.ku.dk/"
format:
  html: default
  academic-typst:
    section-numbering: "1.1.1"
    columns: 2
    papersize: a4
    margin:
      x: 2cm
      y: 2cm
format-links:
  - html
  - format: academic-typst
    text: PDF
    icon: file-pdf
abstract: |
  **Background**: Greater, more extensive collaboration is increasingly needed
  in the modern research environment, often to the level of team-based science.
  Combined with this need is the emphasize on doing more open science. However,
  there seems to be less attention on the overlap between open science and
  collaboration.

### 2025-03-18 doc/protocol.qmd
chore: :wrench: add ORCID and affiliation URLs (#114)
Closes #109, closes #110

---
title: "Towards open collaboration in biomedical and health research: A protocol for a scoping review of open collaboration"
date: "2022-11-04"
author: 
  - name: Hannah Chatwin
    affiliations: 
      - ref: au
  - name: Mario Garcia
    affiliations: 
      - ref: ku
  - name: Daniel B. Ibsen
    orcid: "0000-0002-7038-4770"
    affiliations: 
      - ref: sdca
      - ref: au
  - name: Luke W. Johnston
    orcid: "0000-0003-4169-2616"
    affiliations: 
      - ref: sdca
      - ref: au
affiliations:
  - id: sdca
    name: Steno Diabetes Center Aarhus
    country: Denmark
    url: "https://www.stenoaarhus.dk/"
  - id: au
    name: Aarhus University
    country: Denmark
    url: "https://www.au.dk/"
  - id: ku
    name: Copenhagen University
    country: Denmark
    url: "https://www.ku.dk/"
doi: 10.17605/OSF.IO/K9DR5
execute:
  echo: false
format:
  html: default
  typst:
    columns: 2
    papersize: a4
    margin:
      x: 2cm
      y: 2cm
format-links:
  - html
  - format: typst
    text: PDF
    icon: file-pdf
---

>>>>

---
title: "Towards open collaboration in biomedical and health research: A protocol for a scoping review of open collaboration"
date: "2022-11-04"
author: 
  - name: Hannah Chatwin
    affiliations: 
      - ref: au
  - name: Mario Garcia
    orcid: "0000-0002-3376-9460"
    affiliations: 
      - ref: ku
  - name: Daniel B. Ibsen
    orcid: "0000-0002-7038-4770"
    affiliations: 
      - ref: sdca
      - ref: au
  - name: Luke W. Johnston
    orcid: "0000-0003-4169-2616"
    affiliations: 
      - ref: sdca
      - ref: au
affiliations:
  - id: sdca
    name: Steno Diabetes Center Aarhus
    country: Denmark
    url: "https://www.stenoaarhus.dk/"
  - id: au
    name: Aarhus University
    country: Denmark
    url: "https://www.au.dk/"
  - id: ku
    name: Copenhagen University
    country: Denmark
    url: "https://www.ku.dk/"
doi: 10.17605/OSF.IO/K9DR5
execute:
  echo: false
format:
  html: default
  typst:
    columns: 2
    papersize: a4
    margin:
      x: 2cm
      y: 2cm
format-links:
  - html
  - format: typst
    text: PDF
    icon: file-pdf
---
